Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-11 rebuttal.tex

\comment{Proteochemometric methods are mentioned a couple of times but
  these are largely un-noticed by the community currently. I do not
  think that it is necessarily appropriate to include these as
  tried-and-tested methods in an over-arching review such as this.}
\response{While it is true that proteochemometric methodologies are
  not as well known as say docking or pharmacophore modeling, we
  choose to include them since they are an example of a (statistical)
  QSAR technique that does explicitly include ligand and receptor features}

\comment{RDKit is not mentioned at all in this article and is widely
  used as a cheminformatics toolkit in industry and academia and free
  and open-source (although from commercial beginnings).}
\response{We agree that this toolkit should have been included. We
  have updated the text on page 7 to take note of RDKit, though we
  still primarily focus on the CDK and OpenBabel. However, Table 2
  includes RDKit in the feature comparison}

\comment{The authors could more appropriately cover the graph theory
  aspects of molecular structures by correctly applying the
  terminology to which computer scientists and cheminformaticians will
  most certainly be aware}
\response{The text has been updated}

\comment{p2, c1: I think the authors could benefit from a re-write of
  the section detailing molecular structure representations. \ldots
  Figure 1: what is meant by 'closer to reality' This needs to be
  clarified. This figure and its caption requires a little more
  consideration to appropriately convey the message, }
\response{We have updated the caption to remove the phrase ``closer to
  reality'' since this is not the main point. Instead we have noted
  that the representations contain differing amounts and types of
  information that are equally valid, but suited for different
  purposes. The text on page 2 has been updated to better represent
  this view}

### 2011-11-11 paper.tex
more updates

A key challenge in chemical data mining is the choice of
representation and how that can affect subsequent analysis
efforts. But even after one has been chosen, one faces the challenge
of balancing computational costs with the utility of the
representation. For example, a full 3D description of a molecule,
taking into account all possible conformers would let us accurately
predict many properties. But the size of this representation and the
time required to evaluate it would be prohibitive. Instead, can we
obtain accurate predictions from a subset of conformers? Or, can we
obtain comparable accuracy by using a 2D representation? And is so,
what type of labels are required? Currently, many of these questions
are answered using trial and error.

>>>>

Given that a fundamental principle of the field is that \emph{similar
  molecules exhibit similar properties} \cite{Johnson:1990qf}, the
choice of representation is key in determining how such similarities
are evalaued, and thus the effectiveness of subsequent analyses. But
even after one has selected a representation one faces the challenge
of balancing computational costs with the utility of the
representation. For example, a full 3D description of a molecule,
taking into account all possible conformers would let us accurately
predict many properties. But the size of this representation and the
time required to evaluate it would be prohibitive. Instead, can we
obtain accurate predictions from a subset of conformers? Or, can we
obtain comparable accuracy by using a 2D representation? And is so,
what type of labels are required? Currently, many of these questions
are answered using trial and error.
